### 2013-09-18 Paper_Markdown.Rmd
Fixed regional plotting.

ggplot(data = map, aes(long, lat, group=group)) + geom_path(color='black') +
   coord_map(xlim=c(-170, -40), ylim=c(20, 83))

plot(climate[,2:3], pch=19, cex=0.6, col=rgb(0.1, 0.1, 0.1, 0.3))

>>>>

map <- subset(map, map$long > -170 & map$long < -40)
map <- subset(map, map$lat > 20 & map$lat < 83)

ggplot(data = data.frame(map), aes(long, lat)) + geom_path(aes(group=group), color='black') +
  geom_point(data = data.frame(climate), aes(x = LONDD, y = LATDD)) +
  coord_map(xlim=c(-170, -40), ylim=c(21, 83))
